### 2015-05-27 technical-background.tex
colors
something on the OSI model

% Present the TCP/IP layering
The RFC 1122~\cite{rfc1122} defines the TCP/IP and OSI stack as in the table~\ref{tab:tcp-ip-stack}.
The main difference between the two is the application layer of the TCP/IP stack which corresponds to the three upper layers of the OSI model.
Some references, such as~\citet{tanenbaum2011}, conceptually split the TCP/IP link layer into an additional physical layer.

@@

\noindent The IKEv2 protocol uses four different types of exchanges to fulfill its role:
\begin{itemize}
	\item \texttt{IKE\_SA\_INIT}: The two peers agree on cryptographic parameters to use. Among these is a Diffie-Hellman shared secret from which are derived symmetric keys used for a special IKE SA.
	\item \texttt{IKE\_AUTH}: Once the peers are protected by the IKE SA, they can authenticate themselves to each other and add a first SA in the SA database (SADB).
	The protocol supports three types of authentication methods:
	\begin{itemize}
		\item Digital signature using a PKI.
		\item MAC using a pre-established secret key.
		\item Extensible Authentication Protocol (EAP) defined in~\citet{rfc3748}.
	\end{itemize}
	At this point, the connection is fully established and ready to use.
	\item \texttt{CREATE\_CHILD\_SA}: Used to create new SAs between the two peers. It may involve new generations of DH secrets to ensure perfect forward secrecy.
	\item \texttt{INFORMATIONAL}: Exchange of management information.
\end{itemize}\newline{}

>>>>

% Present the TCP/IP layering
Computer networks are described by two models: the TCP/IP stack and the OSI model, each splitting the network workflow into more or less abstract layers.
The RFC 1122~\cite{rfc1122} defines the TCP/IP, and the international standard ISO/IEC 7498-1~\cite{ISOIEC7498} defines the OSI stack as in the table~\ref{tab:tcp-ip-stack}.
The main difference between the two is the application layer of the TCP/IP stack which corresponds to the three upper layers of the OSI model.
Some references, such as~\citet{tanenbaum2011}, conceptually split the TCP/IP link layer into an additional physical layer.

@@

\noindent The IKEv2 protocol uses four different types of exchanges to fulfill its role:
\begin{itemize}
	\item \texttt{IKE\_SA\_INIT}: The two peers agree on cryptographic parameters to use. Among these is a Diffie-Hellman shared secret from which are derived symmetric keys used for a special IKE SA.
	\item \texttt{IKE\_AUTH}: Once the peers are protected by the IKE SA, they can authenticate themselves to each other and add a first SA in the SA database (SADB).
	The protocol supports three types of authentication methods:
	\begin{itemize}
		\item Digital signature using a PKI.
		\item MAC using a pre-established secret key.
		\item Extensible Authentication Protocol (EAP) defined in~\citet{rfc3748}.
	\end{itemize}
	At this point, the connection is fully established and ready to use.
	\item \texttt{CREATE\_CHILD\_SA}: Used to create new SAs between the two peers. It may involve new generations of DH secrets to ensure perfect forward secrecy.
	\item \texttt{INFORMATIONAL}: Exchange of management information.
\end{itemize}
~\newline{}
